---
title: "How variable are quality and cost of living?"
author: "Cesar Nillaga"
date: "4/26/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(httr)
library(jsonlite)
library(tidyverse) 
library(gganimate)
```


### San Diego vs. San Luis Obispo

The following information is from the Teleport API linked below. 

[Teleport API](https://developers.teleport.org/api/)


```{r, echo=FALSE}
res = GET("https://api.teleport.org/api/urban_areas/slug:san-diego/scores/")
data <- fromJSON(rawToChar(res$content))
```


```{r, echo=FALSE}
df <- data$categories      # getting quality livings from API for San Diego 

df <- df %>%                             
   arrange(score_out_of_10) %>%            # arranging scores in descending order 
   mutate(name = factor(name, name))       # making name a factor for visualization
```

San Diego, California, is among the top cities with a **free business environment**. According to our city rankings, this is a good place to live with high ratings in **startups**, **venture capital** and **safety**. San Diego is one of the top ten city matches for 1.4% of Teleport users. 

```{r, echo=FALSE}
df %>%
  ggplot(aes(x = name, y = score_out_of_10)) +                                
  geom_segment(aes(x = name, xend = name, y = 0, yend = score_out_of_10), color = "grey") +      
  geom_point(size = 3, color = "#f3c32c") +
  coord_flip() +
  theme_classic()+
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  ) +
  xlab("") +
  ylab("Ranking") + 
  ggtitle("San Diegos Ranking of Quality of living")
```




```{r, echo=FALSE}
res1 = GET("https://api.teleport.org/api/urban_areas/slug:san-luis-obispo/scores/")
data1 <- fromJSON(rawToChar(res1$content))
```



```{r, echo=FALSE}
df1 <- data1$categories      # getting quality livings from API for San Luis Obispo

df1 <- df1 %>%                             
   arrange(score_out_of_10) %>%            # arranging scores in descending order 
   mutate(name = factor(name, name))       # making name a factor for visualization
```

San Luis Obispo, California, is among the top cities with a **free business environment**. According to our city rankings, this is a good place to live with high ratings in **safety**, **healthcare** and **environmental quality**. 

```{r, echo=FALSE}
df1 %>%
  ggplot(aes(x = name, y = score_out_of_10)) +                                
  geom_segment(aes(x = name, xend = name, y = 0, yend = score_out_of_10), color = "grey") +      
  geom_point(size = 3, color = "#36cc24") +
  coord_flip() +
  theme_classic()+
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  ) +
  xlab("") +
  ylab("Ranking") + 
  ggtitle("San Luis Obispo Ranking of Quality of living")
```

